The effects of binarity on planet occurrence rates measured by transit surveys

### 2017-11-29 sandbox/note_km.tex
add twin binary, planet distrbn case

We have $f(q)=\delta(q-1)$. The apparent rate is
\begin{align}
\Lambda\a(r\a)
={1\over 1+\mu(\mathrm{BF})}
\left\{\Lambda_0(r\a)
+\mu(\mathrm{BF})\cdot \sqrt{2}\cdot\left[\Lambda_1(\sqrt{2}\,r\a)
+\Lambda_2(\sqrt{2}\,r\a)\right]
\right\},
\end{align}
where
\begin{equation}
	\mu(\mathrm{BF})=\int \mathrm{d}q\,f(q) 
	{\mathrm{BF}\over{1-\mathrm{BF}}}\left[1+{L(qM\a) \over 
	L(M\a)}\right]^{3/2}
	=2^{3/2}\cdot{\mathrm{BF}\over{1-\mathrm{BF}}}.
\end{equation}

@@

>>>>

We have $f(q)=\delta(q-1)$. The apparent rate is
\begin{align}
\Lambda\a(r\a)
={1\over 1+\mu(\mathrm{BF})}
\left\{\Lambda_0(r\a)
+\mu(\mathrm{BF})\cdot \sqrt{2}\cdot\left[\Lambda_1(\sqrt{2}\,r\a)
+\Lambda_2(\sqrt{2}\,r\a)\right]
\right\},
\label{eq:apparent_rate_twin_binary}
\end{align}
where
\begin{equation}
	\mu(\mathrm{BF})=\int \mathrm{d}q\,f(q) 
	{\mathrm{BF}\over{1-\mathrm{BF}}}\left[1+{L(qM\a) \over 
	L(M\a)}\right]^{3/2}
	=2^{3/2}\cdot{\mathrm{BF}\over{1-\mathrm{BF}}}.
\end{equation}

@@

\subsubsection{Power Law Distribution of Planets}

Imagine instead that we took $\Lambda_i(r,M) = Z_i r^\delta$.
From Eq.~\ref{eq:apparent_rate_twin_binary}, we get an apparent rate
\begin{equation}
\Lambda_a(r_a) = r_a^\delta \left[
\frac{Z_0}{1+\mu({\rm BF})}
+
2^{\frac{\delta}{2} + 1 } \frac{\mu({\rm BF})}{1+\mu({\rm BF})} \left(
Z_1 + Z_2
\right)
\right].
\end{equation}

Consider the case when the $Z_i$'s are identical. If we compare 
$\Lambda_a(r_a)$ with $\Lambda(r)$, we must impose that $r_a$ and $r$ are 
indistinguishable (i.e.: the observer cannot tell them apart).
Note that the true rate is
\begin{equation}
\Lambda(r) = r^\delta \left[
\frac{Z_0}{1+2\mu} + \frac{\mu}{1+2\mu} (Z_1+Z_2)
\right]
\end{equation}
We then get a correction factor
\begin{equation}
X_\Lambda \equiv \left. \frac{\Lambda_a(r_a)}{\Lambda(r)} 
\right|_{r_a\rightarrow r}
=
\frac{2^{\frac{\delta}{2}+2}\mu + 1}{\mu + 1}.
\end{equation}

For the case of ${\rm BF}=0.1$, $\mu\approx 0.153$. Taking $\delta=-2.92$ from 
Howard et al. (2012),  we get a correction factor $X_\Lambda = 
\Lambda_a/\Lambda = 1.06$.
In other words, the apparent rate is an {\it over}estimate of the true rate, 
with a relative error of 6\%.
